Deployable Probabilistic Programming

### 2019-04-16 paper/paper.tex
removed listings-golang, included inline in the paper

>>>>

Performing inference as an integral part of algorithms of a
production software system poses challenges to the probabilistic
programming facility. To address the challenges, we proposed
guidelines for implementation of a deployable probabilistic
programming facility. Infergo, a probabilistic programming
facility in Go, is a reference implementation following 
the guidelines.
